### 2013-05-14 inst/examples/gaussian-process-basics.Rmd
replicate run

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA)
library(ggplot2) # plotting 
opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=10))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
```

@@

```{r}
fig2a <- ggplot(dat,aes(x=x,y=value)) +
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-2, ymax=2, fill="grey80") +
  geom_line(aes(group=variable)) +  
  scale_y_continuous(lim=c(-3,3), name="output, f(x)") +
  xlab("input, x")
fig2a
```

@@

```{r}
dat <- data.frame(x=x_predict, t(values))
dat <- melt(dat, id="x")

@@

@@

```{r}
dat <- data.frame(x=x_predict, t(values))
dat <- melt(dat, id="x")
Ey <- data.frame(x=x_predict, y=(Ef), ymin=(Ef-2*sqrt(diag(Cf))), ymax=(Ef+2*sqrt(diag(Cf))))

@@

```{r}
postdist <- cbind(index=1:n, as.data.frame(exp(out$batch)))
names(postdist) <- c("index", names(pars))
df <- melt(postdist, id="index")
# TRACES
ggplot(df) + geom_line(aes(index, value)) + facet_wrap(~ variable, scale="free", ncol=1)

@@

>>>>

```{r plotting-options}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA, dev="CairoPDF", fig.width=6, fig.height=4)
library(ggplot2) # plotting 
opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=10))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
               "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

@@

```{r fig2a}
fig2a <- ggplot(dat,aes(x=x,y=value)) +
  geom_rect(xmin=-Inf, xmax=Inf, ymin=-2, ymax=2, fill="grey80") +
  geom_line(aes(group=variable)) +  
  scale_y_continuous(lim=c(-3,3), name="output, f(x)") +
  xlab("input, x")
fig2a
```

@@

```{r fig2b}
dat <- data.frame(x=x_predict, t(values))
dat <- melt(dat, id="x")

@@

```{r fig2_data}
ggplot(data=obs,aes(x=x,y=y)) +
  geom_point()   #OBSERVED DATA
```

@@

```{r fig2c}
dat <- data.frame(x=x_predict, t(values))
dat <- melt(dat, id="x")
Ey <- data.frame(x=x_predict, y=(Ef), ymin=(Ef-2*sqrt(diag(Cf))), ymax=(Ef+2*sqrt(diag(Cf))))

@@

```{r gp_mcmc}
postdist <- cbind(index=1:n, as.data.frame(exp(out$batch)))
names(postdist) <- c("index", names(pars))
df <- melt(postdist, id="index")
# TRACES
ggplot(df) + geom_line(aes(index, value)) + facet_wrap(~ variable, scale="free", ncol=1)

@@

```{r gp_posteriors}
